%-------------------------
% Resume in Latex
% Author: Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Cyun-Kai (Eddie) Lin} \\ \vspace{1pt}
    % 11F-1, No.509, Dehua St., North Dist., Taichung City 404, Taiwan \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +1 (412)\ 726-4525 ~ 
    \href{mailto:eddielin0926@gmail.com}
    {\raisebox{-0.1\height}\faEnvelope\  eddielin0926@gmail.com} ~ 
    \href{https://www.linkedin.com/in/cyun-kai-lin}{\raisebox{-0.1\height}\faLinkedin\ linkedin.com/in/cyun-kai-lin} ~
    \href{https://github.com/eddielin0926}{\raisebox{-0.1\height}\faGithub\ github.com/eddielin0926}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Carnegie Mellon University}{May. 2024 -- Dec. 2025}
      {M.S. in Information Networking | GPA: 3.91}{Pittsburgh, PA, USA}
      \resumeItem{Coursework: Distributed Systems, Networking and the Internet, Advance Cloud Computing, Database Systems}
    \resumeSubheading
      {National Cheng Kung University}{Sep. 2019 -- June 2023}
      {B.S. in  Computer Science and Information Engineering | GPA: 3.98}{Tainan City, Taiwan}
      \resumeItem{Coursework: Software Design, Linux Kernel Internals, Computer System and Network Administration}
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Appier}{Mar. 2024 -- Aug. 2024}
      {Frontend Engineer}{Taipei City, Taiwan}
      \resumeItemListStart
        \resumeItem{Developed scalable React components as part of a larger design system, prioritizing reusability and maintainability.}
        \resumeItem{Automated updates for internationalization translations from Lokalise, reducing manual code changes.}
        \resumeItem{Enhanced GitHub Actions for Google Cloud Storage by optimizing file parsing, accelerating our deployment speed.}
        \resumeItem{Implemented End-to-End testing with Playwright and deployed coverage reports to GCS, linking them in pull requests.}
      \resumeItemListEnd

    \resumeSubheading
      {Microsoft}{July 2022 -- Dec. 2023}
      {Research and Development Intern}{Taipei City, Taiwan}
      \resumeItemListStart
        \resumeItem{Developed a ROS package enabling low-latency SignalR connections between HoloLens2 and real-time robot interaction.}
        \resumeItem{Presented a robotic arm remote control system in mixed reality at Microsoft DevDays Asia 2022.}
        \resumeItem{Created MR use cases with Azure Digital Twin to improve remote control and monitoring experiences.}
        \resumeItem{Engineered a project with NVIDIA Omniverse to simulate and monitor real-time robot movements and status.}
      \resumeItemListEnd

    % \resumeSubheading
    %   {National Cheng Kung University}{Feb. 2021 -- Dec. 2023}
    %   {Teaching Assistant, Windows Programming, Prof. Jui-Hung Chang}{Tainan City, Taiwan}
    %   \resumeItemListStart
    %     \resumeItem{Taught undergraduate students how to design Windows applications using C\# and develop games with Unity.}
    %     \resumeItem{Conducted over 500 undergraduate students and received positive feedback from students and faculty members.}
    % \resumeItemListEnd

    \resumeSubheading
      {National Cheng Kung University}{Mar. 2023 -- Dec. 2023}
      {Research Assistant}{Tainan City, Taiwan}
      \resumeItemListStart
        \resumeItem{Collaborated with Ministry of Health and Welfare (Taiwan) to set up the classification system for death causes.}
        \resumeItem{Achieved 91\% accuracy in selecting suitable diseases from 40k International Classification of Diseases (ICD)}
    \resumeItemListEnd

    % \resumeSubheading
    %   {National Cheng Kung University}{Aug. 2021 -- June 2022}
    %   {Research Assistant, Computer \& Internet Architecture Lab, Prof. Yeim-Kuan Chang}{Tainan City, Taiwan}
    %   \resumeItemListStart
    %     \resumeItem{Researched and developed a gateway module for Automotive Open System Architecture (AUTOSAR).}
    % \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://official.ainimal.io/}{\textbf{AInimal}} $|$ \emph{React Native, Express, Docker}}{Dec. 2021}
          \resumeItemListStart
            \resumeItem{Worked on developing a dating app, which utilize deep learning model to match users by their personality.}
            \resumeItem{Contributed to developing a dating app boasting 10,000 active users and over 600,000 messages.}
            \resumeItem{Developed three major update features for the dating app, resulting in a 4,000-user increase in one year.}
            \resumeItem{Maintained over 100 backend unit tests, including database operation and API functionality tests.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\href{https://github.com/eddielin0926/kaggle-plus}{\textbf{Kaggle Plus}} $|$ \emph{Typescript, Bun}}{Mar. 2023}
          \resumeItemListStart
            \resumeItem{Developed Kaggle Plus, a browser extension enhances the Kaggle competition experience by visualizing leaderboards.}
            \resumeItem{Released Kaggle Plus on the Google Web Store, offering enhanced features with a stable, growing user base.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------INVOLVEMENT---------------
\section{Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{Google Developer Student Club}{Sep. 2022 -- June 2023}{Core Team Member}{National Cheng Kung University}
            \resumeItemListStart
                \resumeItem{Guiding team members implemented unit tests for projects and integrated tests into CI/CD pipelines on GCP.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------AWARDS---------------
\section{Awards}
    \resumeSubHeadingListStart
        \resumeSubheading{\href{https://nci.org.au/news-events/news/growing-skills-hpc-researchers-through-regional-competition}{Asia-Pacific HPC-AI Competition}}{Nov. 2022}{Third Place \& Best Deep Learning Performance -- among 24 teams across 12 countries}{HPC-AI Advisory Council}
        \resumeSubheading{\href{https://news.microsoft.com/zh-tw/features/microsoft-hackathon-2022/}{Microsoft Global Hackathon}}{Oct. 2022}{Award Winner -- the top project of mixed reality in global}{Microsoft}
        % \resumeSubheading{\href{https://www.csie.ncku.edu.tw/zh-hant/news/12560}{Integrated Circuit Design Contest}}{May 2023}{Honorable Mention Award -- the top 5 teams among 131 teams in Taiwan}{Ministry of Education, Taiwan}
    \resumeSubHeadingListEnd
\vspace{-12pt}

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.0in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: C, C++, C\#, Python, JavaScript, TypeScript, Go, Java, Verilog, Rust, Scala} \\
     \textbf{Frameworks}{: React, React Native, Vue, FastAPI, Express, .NET, MRTK, Jest, Expo, Pytorch, Gin, Playwright, Storybook} \\
     \textbf{Technologies}{: Docker, Kubernetes, Node.js, HPC, ROS, CI/CD, Azure, GCP, Unity, HoloLens, Omniverse, Nx, Turborepo} \\
    }}
 \end{itemize}
 \vspace{-16pt}

\end{document}
